Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 trunk/paper_enahpc14/paper.tex
WS: proofread

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}
%
\smartqed
%
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{units}
\usepackage{color}
\usepackage{colortbl}
\usepackage{xspace}
%
\DeclareRobustCommand\IPCClongname{}
\setcounter{secnumdepth}{5}
%
% please place your own definitions here and don't use \def but \newcommand{}{}
\newcommand{\pmlib}{\texttt{pmlib}\xspace}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical weather  prediction \and Atmospheric
  chemistry  \and  Aerosols  modelling  \and  Profiling  methods  \and
  Benchmark  analysis  \and   \textsc{COSMO-ART}  coupled  model  \and
  Time-to-solution \and Energy-to-solution \and Xeon processor}
% \PACS{PACS code1 \and PACS code2 \and more} 
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}
%
\smartqed
%
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{units}
\usepackage{color}
\usepackage{colortbl}
\usepackage{xspace}
\usepackage{epsfig}
%
\DeclareRobustCommand\IPCClongname{}
\setcounter{secnumdepth}{5}
%
% please place your own definitions here and don't use \def but \newcommand{}{}
\newcommand{\pmlib}{\texttt{pmlib}\xspace}
\newcommand{\monch}{\textsc{Monch}\xspace}
\newcommand{\pilat}{\textsc{Pilatus}\xspace}
\newcommand{\tinto}{\textsc{Tintorrum}\xspace}
\newcommand{\cosmoart}{\textsc{Cosmo-Art}\xspace}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical weather  prediction \and Atmospheric
  chemistry  \and  Aerosol  modelling  \and  Profiling  methods  \and
  Benchmark  analysis  \and   \textsc{COSMO-ART}  coupled  model  \and
  Time-to-solution \and Energy-to-solution \and Xeon processor}
% \PACS{PACS code1 \and PACS code2 \and more} 
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
